R for Clinical Study Reports and Submission

### 2023-07-09 tlf-overview.qmd

- provide simple "verb" functions that correspond to each component of a table,
  to help you translate a data frame to a table in an RTF file;
- enable pipes (`|>`);
- focus on the **table format** only. Data manipulation and analysis tasks can be handled by other R packages like the tidyverse

@@

Functions provided by the r2rtf package are designed to work seamlessly with the pipe operator (|>). This allows for a more concise and readable code structure, enhancing the efficiency of table creation in RTF format.
A full list of functions in the r2rtf package can be found in the
[package reference page](https://merck.github.io/r2rtf/reference/index.html).

Here is a minimal example that demonstrates how to combine functions using pipes to create an RTF table

- `rtf_body()` is used to define table body layout.
- `rtf_encode()` transfers table layout information into RTF syntax.
- `write_rtf()` save RTF encoding into a file with file extension `.rtf`

@@

In the previous example, we may want to add more column space to the first column.
We can achieve the goal by updating the `col_rel_width argument` in the rtf_body() function.

@@

Within the `rtf_colheader()` function, the `colheader` argument is used to specify the content of the column header. 
The columns are separated using the "|" symbol.
In the following example, we define the column header as `"Adverse Events | Placebo | Xanomeline High Dose | Xanomeline Low Dose"`, representing the four columns in the table:

@@

::: {.callout-note}
 the r2rtf package supports 26 different border types, each offering unique border styles. For more details and examples regarding these border types, you can refer to the [r2rtf package website](https://merck.github.io/r2rtf/articles/rtf-row.html#border-type.
:::

>>>>

- Provide simple "verb" functions that correspond to each component of a table,
  to help you translate a data frame to a table in an RTF file.
- Enable pipes (`|>`).
- Focus on the **table format** only. Data manipulation and analysis tasks
  can be handled by other R packages like the tidyverse.

@@

Functions provided by the r2rtf package are designed to work seamlessly
with the pipe operator (`|>`). This allows for a more concise and readable
code structure, enhancing the efficiency of table creation in RTF format.
A full list of functions in the r2rtf package can be found in the
[package reference page](https://merck.github.io/r2rtf/reference/index.html).

Here is a minimal example that demonstrates how to combine functions using
pipes to create an RTF table.

- `rtf_body()` is used to define table body layout.
- `rtf_encode()` transfers table layout information into RTF syntax.
- `write_rtf()` save RTF encoding into a file with file extension `.rtf`.

@@

In the previous example, we may want to add more column space to the first
column. We can achieve the goal by updating the `col_rel_width argument`
in the `rtf_body()` function.

@@

Within the `rtf_colheader()` function, the `colheader` argument is used to
specify the content of the column header.
The columns are separated using the `|` symbol.
In the following example, we define the column header as
`"Adverse Events | Placebo | Xanomeline High Dose | Xanomeline Low Dose"`,
representing the four columns in the table:

@@

::: {.callout-note}
 the r2rtf package supports 26 different border types, each offering unique
 border styles. For more details and examples regarding these border types,
 you can refer to the
 [r2rtf package website](https://merck.github.io/r2rtf/articles/rtf-row.html#border-type).
:::
